### 2016-08-23 notions.tex
cheers

\section{Security Notions}
\label{sec:security-notions}
\tsnote{intro text}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.   
In addition to correctness, we establish three notions of privacy for
set-representations. The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\pubaux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\pubaux,\privaux,q)$ on queries~$q$ of its choosing.  At the end of this game, the adversary must output some point in the set represented by~$M$.  In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two. Then the adversary is given $\pubaux$ and oracle access to $\Qry(M,\pubaux,\privaux,q)$, and it must decide which set~$M$ represents.

@@

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathrm{err}\gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{}{}$.} 
\label{fig:correctness}
\end{figure}

@@

%
%And if the experiment requires the adversary to induce~$r$ errors, the attack wins iff
%$N \stackrel{{\rm def}}{=} \sum_{i=1}^T X_i \geq r$.  Modelling the $X_i$ as independent Bernoulli trials with
%probability~$\epsilon$ gives $N$ a binomial distribution.  \fixme{Something feels wrong with this...}  
%Writing $\bin(T, \epsilon; r)$ for the probability that $N \geq r$,
%we conclude that the \emph{best} correctness we can hope for against adversaries making~$T$ queries is  $\bin(T,\epsilon; t))$. %\jnote{Need to find different terms to use for a query $q \in \mathcal{Q}$
%and a query that the attacker makes to its oracle.}
%\tsnote{Viewed another way, we could let~$T$ be a negative binomial RV, and ask how many queries are needed (w.h.p) for $N \geq t$.} 
%
%\jnote{One option is to define the adversary's \emph{advantage} as the difference between
%its success probability and the success probability of the above,
%trivial attack. Just a thought.}
%\tsnote{Or, perhaps by recasting security
%  as distinguishing between $\Qry(M,\aux,\cdot)$ and an oracle that
%  returns 0,1 according to Bernoulli with paramter~$\epsilon$.}
%\fixme{Not clear this attack is generically applicable enough to serve as a reference/baseline.  (See email discusssion 7/23.)  Might be worth pointing out that this intuition, between non-adaptive error-probability and the expected number of queries to find an error, can be quite misleading.}

@@

\tsnote{Still messing about here, and in the figure.}
In Figure~\ref{fig:privacy-ss} we give a definition capturing semantic-security (of sets)
with respect to the full representation (ss-rep).  In the ``real''
setting (ss-rep-1), a set~$S$ is sampled according to distribution~$\distr{}{}$,
and the adversary is given the~$M,\pubaux$ that result from running
$\Rep(S)$.  It is also provided oracle access to $\TestOracle$.
The adversary must output a function~$f\colon\calS \to \bits^*$ and a
string~$v$ such that $f(S)=v$.  In the ``fake'' setting (ss-rep-0) a
predictor~$P$ is given $\pubaux$ only, and no $\TestOracle$ access.  It
also outputs an $f,v$ pair such that $f(S)=v$.  The advantage of~$A$ (over~$P$)
is $\AdvPrivSS{\Pi,\distr{}{}}{A,P} =
\Prob{\ExpPrivSSreal{\Pi,\distr{}{}}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,\distr{}{}}{P}=1}$.  To prevent trivial wins
for~$A$, e.g. $f(S)=M$, we forbid~$A$ from outputting~$f$
such that $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{}{}$.

@@

\medskip
\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
$S\getsr \distr{}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(f,v) \getsr P(\pubaux)$\\
if $f(S)=v$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
Return~$a$\\
}
}
{
\hpagess{.49}{.49}
{
\experimentv{$\ExpPrivSS{\setprim,\distr{}{},P}{A}$}\\
$S\getsr \distr{}{}$\\
$b \getsr \bits$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(M_1,\pubaux,\privaux) \getsr \Rep(S)$\\
$M_0 \getsr P(\pubaux)$\\
%$(f,v) \getsr \getsr A^{\TestOracle}(M,\pubaux)$\\
$b' \getsr A^{\TestOracle}(M_b,\pubaux)$\\
%if $f(S)=v$ then\\
if $b'=b$ then\\
\nudge Return 1\\
Return 0\\
%
%\medskip
%\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
%$S\getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$(f,v) \getsr P(\pubaux)$\\
%if $f(S)=v$ then\\
%\nudge Return 1\\
%Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M_1,\pubaux,\privaux,q)$\\
Return~$a$\\
}
}
\caption{Semantic-security style privacy
  definitions. \textcolor{red}{On the left, need to protect against
    adversary outputting
    things like $f(S)=M$.  One idea is to forbid~$f$ such that
    $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{}{}$.}
    } 
\label{fig:privacy-ss}
\end{figure}
\subsection{Relationships Among Notions}

\heading{Privacy notions. }
Clearly we have priv $\Rightarrow$ wpriv, tightly and by a simple
reduction.  We should be able to show
\begin{itemize}
%\item ss-rep $\Rightarrow$ ind-qry
%\item ind-qry $\Rightarrow$ ss-rep \tsnote{Not sure about this separation...}
\item ss-rep $\Rightarrow$ priv \emph{for set-multiplicity data
    structures} \tsnote{but probably not in general}
\item \{w\}priv $\not\Rightarrow$ ss-rep
\item wpriv $\not\Rightarrow$ priv \tsnote{$M=S$, or my
    $M=S\setminus \{x\}$ for a random $x\in S$, if you want something
    a bit less trivial. I'm sure there are more natural schemes that
    will separate, too.}
\end{itemize}

\heading{Correctness vs.\ Privacy. }
If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.
\tsnote{My $M=S\setminus\{x\}$ for a random $x \in S$ construction is less trivial (it compresses), but also serves to separate correctness from Priv.}
\tsnote{In general, it isn't clear how to reduce
correctness to the Priv notion.  In the correctness experiment, you
  get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the
  adversary expects~$(M,\aux)$ as input.  Unless the coins of Rep are
  effectively leaked in~$\aux$, you can't reliably produce~$M$
  given~$(S,\aux)$.} 
Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).
\tsnote{Reducing correctness to the weaker version, wPriv, is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ ---remember, queries are not syntactically restricted to set membership!--- and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... and it's not clear how to do a quality reduction.   }

\tsnote{Likewise the other way: the one-wayness adversary does not get~$S$, and yet needs to provide this to the correctness adversary.}

>>>>

\section{Security Notions}
\label{sec:security-notions}
Following NY, we are interested in defining an adaptive (i.e.,
adversarial) notion of correctness.   
In addition to correctness, we establish three notions of privacy for
set-representations. The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\pubaux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\pubaux,\privaux,q)$ on queries~$q$ of its choosing.  At the end of this game, the adversary must output some point in the set represented by~$M$.  In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two. Then the adversary is given $\pubaux$ and oracle access to $\Qry(M,\pubaux,\privaux,q)$, and it must decide which set~$M$ represents.

@@

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathrm{err}\gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.} 
\label{fig:correctness}
\end{figure}

@@

@@

\tsnote{Wet paint...}
In Figure~\ref{fig:privacy-ss} we give a definition capturing semantic-security (of sets)
with respect to the full representation (ss-rep).  In the ``real''
setting (ss-rep-1), a set~$S$ is sampled according to distribution~$\distr{}{}$,
and the adversary is given the~$M,\pubaux$ that result from running
$\Rep(S)$.  It is also provided oracle access to $\TestOracle$.
The adversary must output a function~$f\colon\calS \to \bits^*$ and a
string~$v$ such that $f(S)=v$.  In the ``fake'' setting (ss-rep-0) a
predictor~$P$ is given $\pubaux$ only, and no $\TestOracle$ access.  It
also outputs an $f,v$ pair such that $f(S)=v$.  The advantage of~$A$ (over~$P$)
is $\AdvPrivSS{\Pi,\distr{}{}}{A,P} =
\Prob{\ExpPrivSSreal{\Pi,\distr{}{}}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,\distr{}{}}{P}=1}$.  To prevent trivial wins
for~$A$, e.g. $f(S)=M$, we forbid~$A$ from outputting~$f$
such that $f(S)=f(S')$ for all $S,S'$ in the support of the
distribution $\distr{}{}$.

@@

\medskip
\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
$S\getsr \distr{}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(f,v) \getsr P(\pubaux)$\\
if $f(S)=v$ then\\
\nudge Return 1\\
Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
Return~$a$\\
}
}
{
\hpagess{.49}{.49}
{
\experimentv{$\ExpPrivSS{\setprim,\distr{}{},P}{A}$}\\
$S\getsr \distr{}{}$\\
$b \getsr \bits$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(M_1,\pubaux,\privaux) \getsr \Rep(S)$\\
$M_0 \getsr P(\pubaux)$\\
%$(f,v) \getsr \getsr A^{\TestOracle}(M,\pubaux)$\\
$b' \getsr A^{\TestOracle}(M_b,\pubaux)$\\
%if $f(S)=v$ then\\
if $b'=b$ then\\
\nudge Return 1\\
Return 0\\
%
%\medskip
%\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
%$S\getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$(f,v) \getsr P(\pubaux)$\\
%if $f(S)=v$ then\\
%\nudge Return 1\\
%Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M_1,\pubaux,\privaux,q)$\\
Return~$a$\\
}
}
\caption{Semantic-security style privacy
  definitions. \textcolor{red}{On the left, need to protect against
    adversary outputting
    things like $f(S)=M$.  One idea is to forbid~$f$ such that
    $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{}{}$.}
    } 
\label{fig:privacy-ss}
\end{figure}

\subsection{Relationships Among Notions}\todo{Decide which of these
  statements should have formal theorems and proofs.}
Clearly we have priv $\Rightarrow$ wpriv, tightly and by an obvious
reduction.  The converse is not true, however: consider the previous
construction in which $M = S \setminus \{x\}$ for a random $x \in S$,
and $\pubaux=\privaux=\emptystring$.  We note that this construction
also serves to separate the priv notion from our notion of
correctness.  (It is $1-(1/|S|)$ correct, but has no priv-security.)

Curiously, the trivial scheme that sets $M=S$, $\pubaux=\privaux=\emptystring$ does seem to be both correct and wpriv-secure (up to the element-wise min-entropy of~$S$).
\tsnote{In general, reducing correctness to wPriv is syntactically possible, but not clear how to connect the success events.  In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?  Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.  Then the correctness attacker does what?  Ask some query~$q_z$ related to~$z$ ---remember, queries are not syntactically restricted to set membership!--- and see if the oracle returns the true value $q_z(S)$?  This is pretty complicated... and it's not clear how to do a quality reduction.   }
\tsnote{Likewise the other way: the one-wayness adversary does not get~$S$, and yet needs to provide this to the correctness adversary.}

We should be able to show
\begin{itemize}
\item ss-rep $\Rightarrow$ priv \emph{for set-multiplicity data
    structures} \tsnote{but probably not in general}
\item \{w\}priv $\not\Rightarrow$ ss-rep
\end{itemize}

### 2016-08-23 results.tex
cheers

\section{Achieving Security Notions}
\heading{Correctness. }  Here we give security proofs and attacks with respect to the correctness notions.
\begin{itemize}
\item Show Bloom Filter is correct in the ROM %\jnote{Would be good to show that RO-based Bloom filter is FP-secure.}
\item FP-security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
\item FP-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
\item FP-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
\item ...
\end{itemize}

\heading{Privacy. } Here we give security proofs and attacks with respect to the privacy notions we have defined.
\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
\begin{itemize}
\item Prove that the basic BF, in the ROM, is private.  \tsnote{Not at all surprising, but it is the first result one would want in this area.}

\item As a simple corrolary, show that the basic BF with $h_j(x)=F_K(\langle j,x \rangle)$ is private.  \tsnote{I believe this also shows that the bigram/PRF approach examined by Neidermayer et al.\ is secure when the hash functions are the $h_j(x)$ just described. }

@@

\item Cast Neidermayer et al.\ attacks on the bigram/PRF-based double-hashing construction (see their paper) into our formalism.  \tsnote{Note that their attack would allow one to recover \emph{every} name, not just one.} \tsnote{Note that Neidermayer et al.\ suggest ditching the double-hashing construction in favor of independent PRFs, so the previous item basically explores their suggestion.}

@@

\item Show implications and/or separations between FP and privacy notions.

>>>>

\section{Achieving Security Notions}
\todo{Below are two lists of things that we should show.}

\heading{Correctness. }  Here we give security proofs and attacks with respect to the correctness notions.
\begin{itemize}
\item Show Bloom Filter is correct in the ROM %\jnote{Would be good to show that RO-based Bloom filter is FP-secure.}
\item correctness security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
\item correctness-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
\item correctness-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
\item ...
\end{itemize}

\heading{Privacy. } Here we give security proofs and attacks with respect to the privacy notions we have defined.
\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the element wise min-entropy of $\distr{}{}$.}
\begin{itemize}
\item Prove that the basic BF, in the ROM, is private.  \tsnote{Relative the strongest notion for which this is true.  If it isn't true for all, then give the attack(s).}

\item As a simple corrolary, show that the basic BF with $h_j(x)=F_K(\langle j,x \rangle)$ is private.  \tsnote{I believe this also shows that the bigram/PRF approach examined by Neidermayer et al.\ is secure when the hash functions are the $h_j(x)$ just described.  This was, in fact, one of the countermeasures they proposed. }

@@

\item Cast Neidermayer et al.\ attacks on the bigram/PRF-based double-hashing construction (see their paper) into our formalism.  \tsnote{Note that their attack would allow one to recover \emph{every} name, not just one.}

@@

\item Show implications and/or separations between FP and privacy notions. \tsnote{Belongs in previous section.}
